Twisted 11-dimensional supergravity, I

### 2021-09-13 draft.tex
index

>>>>

As a first consistency check, we can compare deformation invariants attached to the holomorphic twist and Poisson Chern-Simons. We will find a match between indices counting local operators supported at a point.

Consider the cartan subalgebra of the bosonic part of $\lie{osp}(6|1)$. Explicitly, the action of this subalgebra on the fields of the holomorphic twist is induced from an action on $\C^5$ with weights as in the following table

\begin{tabluar}

\end{tabular}
